Co-moving stars in \textsl{Gaia DR1}: a catalog of genuine comoving star pairs from low-resolution spectroscopic follow-up

### 2017-05-30 paper/comoving-followup.tex
omg the most boring words ever written

\author{Melissa~Ness}
\affiliation{todo}

@@

@@

@@

\acknowledgements
David W. Hogg (NYU)

>>>>

@@

% \author{Melissa~Ness}
% \affiliation{todo}

@@

Spectra were obtained using the \project{Modspec} spectrograph mounted on the
$2.4~{\rm m}$ Hiltner telescope at MDM
observatory\footnote{\url{http://mdm.kpno.noao.edu}} on Kitt Peak (Arizona).
\project{Modspec} was set up in long-slit mode with a 1'' slit, a $600~{\rm
line}~{\rm mm}^{-1}$ grating, and a $2048\times2048~{\rm pixel}$ SITe CCD
detector (``Echelle'').
Only the central 300 pixel columns were read out from the CCD, and pixel rows
$>1600$ (at the blue end) were later trimmed because of the poor quantum
efficiency of the CCD at wavelengths $\lesssim 3600~{\rm \AA}$.
The resolution and wavelength range were $\approx2~{\rm \AA}~{\rm pixel}^{-1}$
from $\approx 3600$--$7200~{\rm \AA}$.
At this resolution, to obtain high signal-to-noise spectra, most exposures were
between $30$--$120~{\rm s}$ (15th and 85th percentiles).
To maximize the number of observed pairs, we therefore chose to not take
comparison lamp spectra at each pointing, which adds an overhead of $\approx
90~{\rm s}$ per observation.
To determine rough nightly wavelength solutions, spectra were obtained using
Hg-Ne and Ne comparison lamps at the beginning and end of each night, and
atmospheric emission lines were used to correct the wavelength solution on a
per-object basis.

We observed a total of 765 unique sources over 5 nights from (UT) 2017-03-11 to
2017-03-15, corresponding to 321 unique star pairs and $\approx 120$ calibration
targets.
The calibration targets have previously measured radial velocities and chemical
abundances, which will be used for validation of our reduction pipeline and in
future work to measure metallicities and stellar parameters for each observed
source using \project{The Cannon} (\citealt{Ness:TODO}).
The spectra were reduced and calibrated using a custom, publicly-available
pipeline written in \python,\footnote{Released along with the code used to
generate the figures in this document at
\url{https://github.com/adrn/GaiaPairsFollowup}.} summarized below.

For each source or comparison lamp observation, the two-dimensional image is
bias corrected, flat-field corrected, and trimmed using standard routines
implemented in \package{ccdproc} (\citealt{Craig:2015}).
For comparison lamp observations, the central 100 pixel columns are extracted
and summed along the spatial axis, weighted by the inverse-variances of each
pixel.
Source spectral traces were always placed in this region during observations,
and the curvature of the wavelength solution over this region is negligible.
For source observations, the 2D spectra are extracted to 1D using an
empirically-estimated line spread function (LSF): at each of 16 pixel rows
between indices 750 and 850 (i.e. around the effective center of the dispersion
axis), a model for the LSF is fit to the 1D trace.
The LSF is assumed to be a Voigt profile with parameters $A$, amplitude; $x_0$,
profile centroid; $\sigma_G$, Gaussian root-variance; $\gamma_L$, Lorentzian
half-width at half maximum, and the background is modeled using a linear
polynomial with parameters $\alpha_1$ and $\alpha_2$, the slope and intercept at
the profile centroid, respectively.
The maximum-likelihood LSF + background model parameters are estimated from each
pixel row using \texttt{L-BFGS-B} optimization (\citealt{Zhu:1994}), implemented
in the \package{scipy} package.
From the 16 fits, the median profile width parameters, $\sigma_G$ and
$\gamma_L$, are then taken to be the LSF width parameters.
At each of 1600 rows in each source image, the LSF amplitude and centroid, and
background slope and intercept at line centroid are then fit using the same
procedure as above but with the width parameters fixed.
The LSF amplitudes are stored as the source fluxes, and the background model
intercepts are stored as the background (sky) fluxes.
Occasionally, nearby sources fall in the slit; these are masked by hand in the
2D images and do not bias the LSF extraction fits.

\package{celerite} (\citealt{Foreman-Mackey:2017})

@@

\acknowledgements
John Brewer (Yale),
Jason Curtis (Columbia),
James Davenport (WWU) for PyDIS,
David W. Hogg (NYU),
Melissa Ness (MPIA)

This work is based on observations obtained at the MDM Observatory, operated by
Dartmouth College, Columbia University, Ohio State University, Ohio University,
and the University of Michigan.
% The authors are pleased to acknowledge that the work reported on in this paper
% was substantially performed at the TIGRESS high performance computer center at
% Princeton University which is jointly supported by the Princeton Institute for
% Computational Science and Engineering and the Princeton University Office of
% Information Technology's Research Computing department.

\software{
The code used in this project is available from
\url{https://github.com/adrn/GaiaPairsFollowup} under the MIT open-source
software license.
This research utilized the following open-source \python\ packages:
    \package{Astropy} (\citealt{Astropy-Collaboration:2013}),
    \package{astroquery} (\citealt{Ginsburg:2016}),
    \package{ccdproc} (\citealt{Craig:2015}),
    \package{celerite} (\citealt{Foreman-Mackey:2017}),
    \package{IPython} (\citealt{Perez:2007}),
    \package{matplotlib} (\citealt{Hunter:2007}),
    \package{numpy} (\citealt{Van-der-Walt:2011}),
    \package{scipy} (\url{https://www.scipy.org/}),
    \package{sqlalchemy} (\url{https://www.sqlalchemy.org/})
}

\facility{MDM: Hiltner (Modspec)}
